---
title: "Tidyverse Assignment"
author: "Maryluz Cruz"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load the Tidyverse Package

```{r}
require(tidyverse)
```

#### Tidyverse::readr

- Using readr to read in the csv file.

```{r}
avengers<-read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv",col_names = TRUE)
```

Data used for this Assignment is from fivethirtyeight Avengers.csv https://github.com/fivethirtyeight/data/blob/master/avengers/avengers.csv


```{r}
str(avengers)
```

#### Tidyverse::dplyr - filter

- Use filter to filter out the number of apperences that are over 1000

```{r}
avengers_1000_over<-filter(avengers,Appearances>1000)
avengers_1000_over
```

- Filter out the the Avengers that are Current

```{r}
avengers_current<-filter(avengers_1000_over,`Current?`=="YES")
avengers_current
```

#### Tidyverse::dplyr - group_by

```{r}
avengers_current %>%
  group_by(`Name/Alias`)%>%
  summarise(Year)

```

#### Tidyverse::dplyr - select

- Here you can select the columns that you want from the table

```{r}
avengers_new_table<-avengers_current%>%
  select(`Name/Alias`,Year,Gender,Appearances, `Years since joining`)
avengers_new_table
```

#### Tidyverse::dplyr - arrange

- Arrange the columns by the number of Appearances in Descending order

```{r}
arrange(avengers_new_table,desc(Appearances))
```

#### Tidyverse::dplyr - mutate with arrange

- Calculate the Average of Appearances and Years since joining and arrange it by Appearances in descending order

```{r}
avengers_new_table%>%
  mutate(Year_Over_Appearances= Appearances/`Years since joining`)%>%
  arrange(desc(Appearances))
```


